---
title: "Competition Experiments - 4/21/23 to 4/28/23"
author: "Marissa Douglas"
date: "2023-05-22"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load packages
```{r}
library(patchwork)
library(dplyr)
library(tidyverse)
```

Upload data of the colony moved to a used box
```{r message=FALSE}
old_box <-read.csv("Competition Experiments - 4_21_23 to 4_28_23  - Tidy Old Box.csv")
head(old_box)
```
Graph the sticks
```{r}
sticks_old <- old_box %>% 
  filter(location == "stick")
```

```{r}
#get the average on each day with mutate
sticks_old <- sticks_old %>% 
  filter(!is.na(count))%>%
  group_by(day) %>% 
  mutate(meanInDay = mean(count))

sticks_old_plot <- sticks_old %>%
  filter(!is.na(count))%>%
  ggplot(aes(x = day, y = meanInDay)) +
  geom_line(aes(), alpha = .2) +
  geom_point() +
  ylim(0,14)+
  xlab("Day of Observation") +
  ylab("Mean Number of Ants on Sticks")
sticks_old_plot 

```
Graph the used nests
```{r}
used_old <- old_box %>% 
  filter(location == "usedNest")
```

```{r}
#get the average on each day with mutate
used_old <- used_old %>% 
  filter(!is.na(count))%>%
  group_by(day) %>% 
  mutate(meanInDay = mean(count))


used_old_plot <- used_old %>%
  filter(!is.na(count))%>%
  ggplot(aes(x = day, y = meanInDay)) +
  geom_line(aes(), alpha = .2) +
  geom_point() +
  ylim(0,3)+
  xlab("Day of Observation") +
  ylab("Mean Ants on Used Nest")

used_old_plot

```
Graph the fresh nests
```{r}
fresh_old <- old_box %>% 
  filter(location == "freshNest")
```

```{r}
#get the average on each day with mutate
fresh_old <- fresh_old%>% 
  filter(!is.na(count))%>%
  group_by(day) %>% 
  mutate(meanInDay = mean(count))


fresh_old_plot<-fresh_old %>%
  filter(!is.na(count))%>%
  ggplot(aes(x = day, y = meanInDay)) +
  geom_line(aes(), alpha = .2) +
  geom_point() +
  ylim(0,9)+
  xlab("Day of Observation") +
  ylab("Mean Ants on Fresh Nest")
fresh_old_plot

```
```{r}
used_old_plot+fresh_old_plot
```
Graph the water

```{r}
water_old <- old_box %>% 
  filter(location == "water")
```

```{r}
#get the average on each day with mutate
water_old <- water_old %>% 
  filter(!is.na(count))%>%
  group_by(day) %>% 
  mutate(meanInDay = mean(count))

water_old_plot<-water_old %>%
  filter(!is.na(count))%>%
  ggplot(aes(x = day, y = meanInDay)) +
  geom_line(aes(), alpha = .2) +
  geom_point() +
  ylim(0,6)+
  xlab("Day of Observation") +
  ylab("Mean Number of Ants on Water")

water_old_plot

```

Graph the sugar water
```{r}
sugar_old <- old_box %>% 
  filter(location == "sugarWater")
```

```{r}
#get the average on each day with mutate
sugar_old <- sugar_old %>% 
  filter(!is.na(count))%>%
  group_by(day) %>% 
  mutate(meanInDay = mean(count))


sugar_old_plot <- sugar_old %>%
  filter(!is.na(count))%>%
  ggplot(aes(x = day, y = meanInDay)) +
  geom_line(aes(), alpha = .2) +
  geom_point() +
  ylim(0,6)+
  xlab("Day of Observation") +
  ylab("Mean Number of Ants on Sugar Water")

sugar_old_plot

```

Graph the napkin slide
```{r}
napkin_old <- old_box %>% 
  filter(location == "napkinSlide")
```

```{r}
#get the average on each day with mutate
napkin_old <- napkin_old %>% 
  filter(!is.na(count))%>%
  group_by(day) %>% 
  mutate(meanInDay = mean(count))


napkin_old_plot <- napkin_old %>%
  filter(!is.na(count))%>%
  ggplot(aes(x = day, y = meanInDay)) +
  geom_line(aes(), alpha = .2) +
  geom_point() +
  ylim(0,3)+
  xlab("Day of Observation") +
  ylab("Mean Number of Ants on Napkin Slide")

napkin_old_plot

```

Graph the pollen and cricket dish
```{r}
pollen_old <- old_box %>% 
  filter(location == "pollenCricket")
```

```{r}
#get the average on each day with mutate
pollen_old <- pollen_old %>% 
  filter(!is.na(count))%>%
  group_by(day) %>% 
  mutate(meanInDay = mean(count))


pollen_old_plot <- pollen_old %>%
  filter(!is.na(count))%>%
  ggplot(aes(x = day, y = meanInDay)) +
  geom_line(aes(), alpha = .2) +
  geom_point() +
  ylim(0,1)+
  xlab("Day of Observation") +
  ylab("Mean Number of Ants on Pollen and Cricket Dish")

pollen_old_plot

```


Graph the other
```{r}
other_old <- old_box %>% 
  filter(location == "other")
```

```{r}
#get the average on each day with mutate
other_old <- other_old %>% 
  filter(!is.na(count))%>%
  group_by(day) %>% 
  mutate(meanInDay = mean(count))


other_old_plot <- other_old %>%
  filter(!is.na(count))%>%
  ggplot(aes(x = day, y = meanInDay)) +
  geom_line(aes(), alpha = .2) +
  geom_point() +
  ylim(0,13)+
  xlab("Day of Observation") +
  ylab("Mean Number of Ants on Other Areas")

other_old_plot

```


```{r message=FALSE}
fresh_box <-read.csv("Competition Experiments - 4_21_23 to 4_28_23  - Tidy New Box.csv")
head(fresh_box)
```



Graph the sticks (new)
```{r}
sticks_new <- fresh_box %>% 
  filter(location == "stick")
```

```{r}
#get the average on each day with mutate
sticks_new <- sticks_new %>% 
  filter(!is.na(count))%>%
  group_by(day) %>% 
  mutate(meanInDay = mean(count))


sticks_new_plot <- sticks_new %>%
  filter(!is.na(count))%>%
  ggplot(aes(x = day, y = meanInDay)) +
  geom_line(aes(), alpha = .2) +
  geom_point() +
  ylim(0,14)+
  xlab("Day of Observation") +
  ylab("Mean Number of Ants on Sticks")
sticks_new_plot

```

Graph the fresh nests (new)
```{r}
fresh_new <- fresh_box %>% 
  filter(location == "freshNest")
```

```{r}
#get the average on each day with mutate
fresh_new <- fresh_new %>% 
  filter(!is.na(count))%>%
  group_by(day) %>% 
  mutate(meanInDay = mean(count))


fresh_new_plot <- fresh_new %>%
  filter(!is.na(count))%>%
  ggplot(aes(x = day, y = meanInDay)) +
  geom_line(aes(), alpha = .2) +
  geom_point() +
  ylim(0,9)+
  xlab("Day of Observation") +
  ylab("Mean Number of Ants on Fresh Nest")
fresh_new_plot

```

Graph the water (new)
```{r}
water_new <- fresh_box %>% 
  filter(location == "water")
```

```{r}
#get the average on each day with mutate
water_new <- water_new %>% 
  filter(!is.na(count))%>%
  group_by(day) %>% 
  mutate(meanInDay = mean(count))


water_new_plot <- water_new %>%
  filter(!is.na(count))%>%
  ggplot(aes(x = day, y = meanInDay)) +
  geom_line(aes(), alpha = .2) +
  geom_point() +
  ylim(0,6)+
  xlab("Day of Observation") +
  ylab("Mean Number of Ants on Water")
water_new_plot
```

Graph the sugar water 
```{r}
sugar_new <- fresh_box %>% 
  filter(location == "sugarWater")
```

```{r}

#get the average on each day with mutate
sugar_new <- sugar_new %>% 
  filter(!is.na(count))%>%
  group_by(day) %>% 
  mutate(meanInDay = mean(count))


sugar_new_plot <- sugar_new %>%
  filter(!is.na(count))%>%
  ggplot(aes(x = day, y = meanInDay)) +
  geom_line(aes(), alpha = .2) +
  geom_point() +
  ylim(0,6)+
  xlab("Day of Observation") +
  ylab("Mean Number of Ants on Sugar Water")
sugar_new_plot

```

Graph the napkin slide 
```{r}
napkin_new <- fresh_box %>% 
  filter(location == "napkinSlide")
```

```{r}
#get the average on each day with mutate
napkin_new <- napkin_new %>% 
  filter(!is.na(count))%>%
  group_by(day) %>% 
  mutate(meanInDay = mean(count))


napkin_new_plot <- napkin_new %>%
  filter(!is.na(count))%>%
  ggplot(aes(x = day, y = meanInDay)) +
  geom_line(aes(), alpha = .2) +
  geom_point() +
  ylim(0,3)+
  xlab("Day of Observation") +
  ylab("Mean Number of Ants on Napkin Slide")
napkin_new_plot

```


Graph the pollen cricket
```{r}
pollen_new <- fresh_box %>% 
  filter(location == "pollenCricket")
```

```{r}
#get the average on each day with mutate
pollen_new <- pollen_new %>% 
  filter(!is.na(count))%>%
  group_by(day) %>% 
  mutate(meanInDay = mean(count))


pollen_new_plot <- pollen_new %>%
  filter(!is.na(count))%>%
  ggplot(aes(x = day, y = meanInDay)) +
  geom_line(aes(), alpha = .2) +
  geom_point() +
  ylim(0,1)+
  xlab("Day of Observation") +
  ylab("Mean Number of Ants on Pollen Cricket")
pollen_new_plot

```

Graph the other
```{r}
other_new <- fresh_box %>% 
  filter(location == "other")
```

```{r}
#get the average on each day with mutate
other_new <- other_new %>% 
  filter(!is.na(count))%>%
  group_by(day) %>% 
  mutate(meanInDay = mean(count))


other_new_plot <- other_new %>%
  filter(!is.na(count))%>%
  ggplot(aes(x = day, y = meanInDay)) +
  geom_line(aes(), alpha = .2) +
  geom_point() +
  ylim(0,13)+
  xlab("Day of Observation") +
  ylab("Mean Number of Ants on Other")
other_new_plot
```


Patchwork interesting comparisons:


In the old/previously inhabited box, compare the number of ants on the used nest vs the fresh nest
```{r}
used_old_plot+fresh_old_plot
```
For each location, compare the counts in the new/fresh box vs the old/prev. inhabited box


sticks in old v new
```{r}
sticks_old_plot+sticks_new_plot
```
fresh nests in new v old
```{r}
fresh_old_plot+fresh_new_plot
```

water in new v old
```{r}
water_old_plot+water_new_plot
```


sugar water in new v old
```{r}
sugar_old_plot+sugar_new_plot
```

napkin slide in new v old
```{r}
napkin_old_plot+napkin_new_plot
```

pollen and cricket dish in new v old
```{r}
pollen_old_plot+pollen_new_plot
```


other locations in new v old
```{r}
other_old_plot+other_new_plot
```

